---
title: "lobster-pictures"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
use_python(Sys.which("python"))
```

## Training a TensorFlow model with R

Based on the guide from [TensorFlow for R from R Studio ](https://tensorflow.rstudio.com/tutorials/beginners/basic-ml/tutorial_basic_classification/)

https://github.com/rstudio/tensorflow

>This guide uses the Fashion MNIST dataset which contains 70,000 grayscale images in 10 categories. The images show individual articles of clothing at low resolution (28 by 28 pixels), as seen here:


### Installation and setup:

Install/Load the required packages:
```{r}
#Uncomment the following line to include the installation of the keras package:
#install.packages("keras")
#install.packages("tensorflow")
```

Load the keras library in to the R session:
```{r}
library(keras)
library(tensorflow)
```

```{r}
#install_tensorflow()
```

You may need to install cuda and anacoda, these instructions from a github user [CostanzoPablo](https://github.com/CostanzoPablo) were helpful in getting tensorflow/stream_executor/platform/default/dso_loader / cudart64_110.dll to work on my machine:

>
- Uninstall all drivers that says "nvidia" from Uninstall programs (ALL, Cuda and gpu driver)
- Install last nvidia drivers for your GPU https://uk.download.nvidia.com/GFE/GFEClient/3.21.0.36/GeForce_Experience_v3.21.0.36.exe
- Install cuda 11.2 https://developer.download.nvidia.com/compute/cuda/11.2.1/local_installers/cuda_11.2.1_461.09_win10.exe
- Install Anaconda https://repo.anaconda.com/archive/Anaconda3-2020.11-Windows-x86_64.exe
- conda create -n cudaenv python=3.6
- conda activate cudaenv
- pip install tensorflow python-dotenv
- Create a.py with this: import tensorflow as tf
- run it: python a.py
- Output:
  xxx: I tensorflow/stream_executor/platform/default/dso_loader.cc:49] Successfully opened dynamic library cudart64_110.dll

https://github.com/tensorflow/tensorflow/issues/45055


### Basic Example: Importing the Fashion MNIST dataset
>Fashion MNIST is intended as a drop-in replacement for the classic MNIST dataset—often used as the “Hello, World” of machine learning programs for computer vision. The MNIST dataset contains images of handwritten digits (0, 1, 2, etc) in an identical format to the articles of clothing we’ll use here.
This guide uses Fashion MNIST for variety, and because it’s a slightly more challenging problem than regular MNIST. Both datasets are relatively small and are used to verify that an algorithm works as expected. They’re good starting points to test and debug code.
We will use 60,000 images to train the network and 10,000 images to evaluate how accurately the network learned to classify images. You can access the Fashion MNIST directly from Keras.

```{r}
fashion_mnist <- dataset_fashion_mnist()
```

```{r}
c(train_images, train_labels) %<-% fashion_mnist$train
c(test_images, test_labels) %<-% fashion_mnist$test
```

```{r}
class_names = c('T-shirt/top',
                'Trouser',
                'Pullover',
                'Dress',
                'Coat', 
                'Sandal',
                'Shirt',
                'Sneaker',
                'Bag',
                'Ankle boot')
```

```{r}
dim(train_images)
```
```{r}
dim(train_labels)
```

```{r}
train_labels[1:20]
```
```{r}
dim(test_images)
```

```{r}
dim(test_labels)
```

```{r}
library(tidyr)
library(ggplot2)
```

### Preprocess the data

```{r}
image_1 <- as.data.frame(train_images[1, , ])
colnames(image_1) <- seq_len(ncol(image_1))
image_1$y <- seq_len(nrow(image_1))
image_1 <- gather(image_1, "x", "value", -y)
image_1$x <- as.integer(image_1$x)

ggplot(image_1, aes(x = x, y = y, fill = value)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "black", na.value = NA) +
  scale_y_reverse() +
  theme_minimal() +
  theme(panel.grid = element_blank())   +
  theme(aspect.ratio = 1) +
  xlab("") +
  ylab("")
```

```{r}
train_images <- train_images / 255
test_images <- test_images / 255
```

```{r}
par(mfcol=c(5,5))
par(mar=c(0, 0, 1.5, 0), xaxs='i', yaxs='i')
for (i in 1:25) { 
  img <- train_images[i, , ]
  img <- t(apply(img, 2, rev)) 
  image(1:28, 1:28, img, col = gray((0:255)/255), xaxt = 'n', yaxt = 'n',
        main = paste(class_names[train_labels[i] + 1]))
}
```

### Build the model

```{r}
model <- keras_model_sequential()
model %>%
  layer_flatten(input_shape = c(28, 28)) %>%
  layer_dense(units = 128, activation = 'relu') %>%
  layer_dense(units = 10, activation = 'softmax')
```

### Compile the model

```{r}
model %>% compile(
  optimizer = 'adam', 
  loss = 'sparse_categorical_crossentropy',
  metrics = c('accuracy')
)
```


### Train the model

```{r}
model %>% fit(train_images, train_labels, epochs = 5, verbose = 2)
```
```{r}
score <- model %>% evaluate(test_images, test_labels, verbose = 0)

cat('Test loss:', score[c("loss")], "\n")
```

```{r}
cat('Test accuracy:', score[c("acc")], "\n")
```

```{r}
predictions <- model %>% predict(test_images)
```

```{r}
predictions[1, ]
```

```{r}
par(mfcol=c(5,5))
par(mar=c(0, 0, 1.5, 0), xaxs='i', yaxs='i')
for (i in 1:25) { 
  img <- test_images[i, , ]
  img <- t(apply(img, 2, rev)) 
  # subtract 1 as labels go from 0 to 9
  predicted_label <- which.max(predictions[i, ]) - 1
  true_label <- test_labels[i]
  if (predicted_label == true_label) {
    color <- '#008800' 
  } else {
    color <- '#bb0000'
  }
  image(1:28, 1:28, img, col = gray((0:255)/255), xaxt = 'n', yaxt = 'n',
        main = paste0(class_names[predicted_label + 1], " (",
                      class_names[true_label + 1], ")"),
        col.main = color)
}
```

```{r}
# Grab an image from the test dataset
# take care to keep the batch dimension, as this is expected by the model
img <- test_images[1, , , drop = FALSE]
dim(img)
```


```{r}
predictions <- model %>% predict(img)
predictions
```

```{r}
# subtract 1 as labels are 0-based
prediction <- predictions[1, ] - 1
which.max(prediction)
```
```{r}
class_pred <- model %>% predict_classes(img)
class_pred
```


## Integrating Python (using Conda) in our R project:

```{r}
conda_install(packages = "wheel")
```

```{r}
conda_install(package = "Pandas")
```

```{r}
conda_install(packages = "tflite_model_maker")
```

```{python}
import pandas
```

```{r}
conda_install(packages = "tflite_model_maker")
```


```{python}
from tflite_model_maker import image_classifier
```
















